District-level cropcover and bias

### 2015-09-22 Rmd/agent-allocation-bias.Rmd
Updated through Results with AW comments.

cexs <- seq(1, 2, 1 / 3)
# pdf(full_path(p_fig, "agent-bias.pdf"), height = 5, width = 3)
pdf(full_path(p_fig, "agent-bias.pdf"), height = 3, width = 5)
cx <- c(0.7, 0.8, 0.6)
# png(full_path(p_fig, "agent-bias.png"), height = 350, width = 700)
# par(mfrow = c(2, 1), mar = c(0.5, 2.5, 0.5, 1), mgp = c(1, 0.05, 0), 
#     tcl = -0.2, oma = c(3.5, 0, 0, 0))
par(mfrow = c(1, 2), mar = c(2, 2, 0.5, 0), mgp = c(0.75, 0.05, 0), 
    tcl = -0.2, oma = c(3.5, 0, 0, 0.1))
scols <- c("red", "orange3", "green4", "blue")
cols <- c(rep("red", 4), rep("orange3", 4), rep("green4", 4), rep("blue", 4))
plot(unlist(pctbias), unlist(noland), col = cols, cex = cexs, pch = 20, 
     ylab = "% HH without farms", xlab = "% cropland bias", cex.lab = cx[2], 
     cex.axis = cx[1])
plot(unlist(pctbias), unlist(unalloc), col = cols, cex = cexs, pch = 20, 
     ylab = "% land unallocated", xlab = "% cropland bias", cex.lab = cx[2], 
     cex.axis = cx[1])
par(xpd = NA)

>>>>

cexs <- seq(1, 2, 1 / 3)
# pdf(full_path(p_fig, "agent-bias.pdf"), height = 5, width = 3)
pdf(full_path(p_fig, "agent-bias.pdf"), height = 3, width = 5)
cx <- c(0.7, 0.8, 0.6)
# png(full_path(p_fig, "agent-bias.png"), height = 350, width = 700)
# par(mfrow = c(2, 1), mar = c(0.5, 2.5, 0.5, 1), mgp = c(1, 0.05, 0), 
#     tcl = -0.2, oma = c(3.5, 0, 0, 0))
par(mfrow = c(1, 2), mar = c(2, 2, 0.5, 0), mgp = c(0.75, 0.05, 0), 
    tcl = -0.2, oma = c(3.5, 0, 0, 0.1))
scols <- c("red", "orange3", "green4", "blue")
cols <- c(rep("red", 4), rep("orange3", 4), rep("green4", 4), rep("blue", 4))
plot(unlist(pctbias), unlist(noland), col = cols, cex = cexs, pch = 20, 
     ylab = "% HH without farms", xlab = "% error in cropland area", 
     cex.lab = cx[2], cex.axis = cx[1])
plot(unlist(pctbias), unlist(unalloc), col = cols, cex = cexs, pch = 20, 
     ylab = "% land unallocated", xlab = "% error in cropland area", 
     cex.lab = cx[2], cex.axis = cx[1])
par(xpd = NA)

### 2015-09-22 Rmd/magisterial-district-bias.Rmd
Updated through Results with AW comments.

ptcols <- sapply(cols, function(x) makeTransparent(x, 80))  # CI colors
lw <- c(rep(2, 4), 3, 3)
yl1 <- c(0, round(max(sapply(gam_mods, function(x) max(x$pdat1$fit))), 1))
yl2 <- c(0, round(max(sapply(gam_mods, function(x) max(x$pdat2$fit))), 1))
pdf(full_path(p_fig, "biases_md_lnorm_gam_mu0.pdf"), width = 7, height = 7)
par(oma = c(0, 0, 0, 0), mar = c(3, 3, 2, 2), mgp = c(1.5, 0.5, 0))
plot(xl, yl2, pch = "", ylab = "% bias", xlab = "% cropland", xaxs = "i",
     mgp = c(1.5, 0.5, 0), yaxs = "i", yaxt = "n")
axis(2, at = 0:4, round(exp(c(-10, 1:4))))
for(i in 1:length(gam_mods)) {
  m <- gam_mods[[i]]
  p <- polyfunc(m$pdat1)
  polygon(p$x, p$y, col = ptcols[i], border = NA)
  lines(fit ~ pv, data = m$pdat1, col = cols[i], lwd = 1.5, lty = 1)
}
legend("topleft", c(mcap, "All 4", "No GlobCover"), lty = 1, lwd = 1.5,
       col = cols, bty = "n", xpd = NA)#, title = "Fit")
dev.off()

pdf(full_path(p_fig, "biases_md_lnorm_gam_med0.pdf"), width = 7, height = 7)
par(oma = c(0, 0, 0, 0), mar = c(3, 3, 2, 2))
plot(xl, yl2, pch = "", ylab = "% bias", xlab = "% cropland", xaxs = "i",
     mgp = c(1.5, 0.5, 0), yaxs = "i", yaxt = "n")
axis(2, at = 0:4, round(exp(c(-10, 1:4))))
for(i in 1:length(gam_mods)) {
  m <- gam_mods[[i]]
  p <- polyfunc(m$pdat2)
  polygon(p$x, p$y, col = ptcols[i], border = NA)
  lines(fit ~ pv, data = m$pdat2, col = cols[i], lwd = 1.5, lty = 1)
}
legend("topleft", c(mcap, "All 4", "No GlobCover"), lty = 1, lwd = 1.5,
       col = cols, bty = "n", xpd = NA)#, title = "Fit")
dev.off()

>>>>

ptcols <- sapply(cols, function(x) makeTransparent(x, 80))  # CI colors
lw <- c(rep(2, 4), 3, 3)
yl1 <- c(0, round(max(sapply(gam_mods, function(x) max(x$pdat1$fit))), 1))
yl2 <- c(0, round(max(sapply(gam_mods, function(x) max(x$pdat2$fit))), 1))
pdf(full_path(p_fig, "biases_md_lnorm_gam_mu0.pdf"), width = 7, height = 7)
par(oma = c(0, 0, 0, 0), mar = c(3, 3, 2, 2), mgp = c(1.5, 0.5, 0))
plot(xl, yl2, pch = "", ylab = "% bias", xlab = "% cropland", xaxs = "i",
     mgp = c(1.5, 0.5, 0), yaxs = "i", yaxt = "n")
axis(2, at = 0:4, round(exp(c(-10, 1:4))))
# for(i in 1:length(gam_mods)) {
for(i in 1:4) {
  m <- gam_mods[[i]]
  p <- polyfunc(m$pdat1)
  polygon(p$x, p$y, col = ptcols[i], border = NA)
  lines(fit ~ pv, data = m$pdat1, col = cols[i], lwd = 1.5, lty = 1)
}
# legend("topleft", c(mcap, "All 4", "No GlobCover"), lty = 1, lwd = 1.5,
#        col = cols, bty = "n", xpd = NA)#, title = "Fit")
legend("topleft", mcap, lty = 1, lwd = 1.5,
       col = cols, bty = "n", xpd = NA)#, title = "Fit")
dev.off()

pdf(full_path(p_fig, "biases_md_lnorm_gam_med0.pdf"), width = 7, height = 7)
par(oma = c(0, 0, 0, 0), mar = c(3, 3, 2, 2))
plot(xl, yl2, pch = "", ylab = "% bias", xlab = "% cropland", xaxs = "i",
     mgp = c(1.5, 0.5, 0), yaxs = "i", yaxt = "n")
axis(2, at = 0:4, round(exp(c(-10, 1:4))))
#for(i in 1:length(gam_mods)) {
for(i in 1:4) {
  m <- gam_mods[[i]]
  p <- polyfunc(m$pdat2)
  polygon(p$x, p$y, col = ptcols[i], border = NA)
  lines(fit ~ pv, data = m$pdat2, col = cols[i], lwd = 1.5, lty = 1)
}
# legend("topleft", c(mcap, "All 4", "No GlobCover"), lty = 1, lwd = 1.5,
#        col = cols, bty = "n", xpd = NA)#, title = "Fit")
legend("topleft", mcap, lty = 1, lwd = 1.5,
       col = cols, bty = "n", xpd = NA)#, title = "Fit")
dev.off()
